---
title: "JatApp - Marketing Analysis"
author: "Andrei Kristov"
date: "11/14/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# JatApp - Marketing Analysis. Data preparation

```{r, include=FALSE,warning=FALSE}
library(tidyverse)
#install.packages("skimr")
library(skimr)
#install.packages("VIM")
library(VIM)
library(lubridate)
#install.packages("dlookr")
#library(dlookr)
#library(dplyr)
```

## Load data
```{r,warning=FALSE}
#load data
market_data <- as_tibble(read.csv("/Users/Andrew/Documents/R/data/JatApp - Marketing analysis/marketing_data.csv", encoding = "utf-8"))

head(market_data)
str(market_data)
```
## Transform data
Income from string to numeric, Dt_Customer to Date, 3,4,21:28 fields - to factors.
```{r,warning=FALSE}
# assign data types to columns
market_data[,c(3,4,21:28)] <-  lapply(market_data[,c(3,4,21:28)],factor)
market_data$Income <- as.numeric(gsub("[$,]","",market_data$Income))
market_data$Dt_Customer <- as.Date(market_data$Dt_Customer,"%m/%d/%y")
str(market_data) 
```
## Missing values
```{r,warning=FALSE}
# Missing values
#skimr::skim(market_data)
missing_values <- market_data %>% summarize_all(funs(sum(is.na(.))/n()))
#head(missing_values)
missing_values <- gather(missing_values, key = "feature", value = "missing_pct")
head(missing_values)
missing_values %>% 
  ggplot(aes(x = reorder(feature, missing_pct), y = missing_pct)) +
  geom_bar(stat = "identity", fill = 'red') +
  coord_flip() + theme_bw()
```

Conclusion: MIssing values in Income. 
```{r,warning=FALSE}
# Impute Income with median by Country+Education
market_data_fixed <- 
  market_data %>%
  group_by(Country, Education) %>%
  mutate(Income_fixed = ifelse(is.na(Income),
                               median(Income, na.rm = T),
                               Income))

# check
# 1 manually, equallity with group median
market_data %>% 
  group_by(Country, Education) %>% summarise(median(Income,na.rm = T))
market_data_fixed %>% filter(is.na(Income)) %>% select(c(Education,Income, Country, Income_fixed))
# 2
sum(is.na(market_data_fixed$Income_fixed))

```
## Save file for use in Power BI
```{r,warning=FALSE}
#write_csv(market_data_fixed,file = "/Users/Andrew/Documents/R/data/JatApp - Marketing analysis/marketing_data_fixed.csv")
```
## Outliers
```{r,warning=FALSE}
# Outliers
summary(market_data_fixed) # outliers in income & income_fixed
#explore outliers by marital status
market_data_fixed %>% 
  select(Marital_Status, Income_fixed) %>%
  ggplot(aes(Marital_Status, Income_fixed, fill=Marital_Status)) + 
  geom_boxplot()+
  scale_fill_brewer(palette = "Set3")
```

Explore outliers by country:
```{r,warning=FALSE}
#explore outliers by country
market_data_fixed %>% 
  select(Country, Income_fixed) %>%
  ggplot(aes(Country, Income_fixed, fill=Country)) + 
  geom_boxplot() +
  scale_fill_brewer(palette = "Set3") +
  scale_y_continuous(labels = scales::dollar)
```

Coclusion: Outliers among Together in SA. Let's leave them.

## Prepare pivoted dataset for visualization in Power BI
```{r,warning=FALSE}
# pivot data on products to investigate shares sold
market_data_fixed_pivoted <- market_data_fixed %>%
  pivot_longer(cols = starts_with("Mnt"), names_to = "Products", values_to = "Amount")
# rename
market_data_fixed_pivoted <- market_data_fixed_pivoted %>%
  mutate(Products = case_when(
    Products == "MntWines" ~ "Wines",
    Products == "MntMeatProducts" ~ "Meat",
    Products == "MntSweetProducts" ~ "Sweet",
    Products == "MntFruits" ~ "Fruits",
    Products == "MntFishProducts" ~ "Fish",
    Products == "MntGoldProds" ~ "Gold",
  ))
head(market_data_fixed_pivoted)
```
## Save pivoted dataset for calculation in Power BI
```{r,warning=FALSE}
# save 
#write.csv(market_data_fixed_pivoted,file = "/Users/Andrew/Documents/R/data/JatApp - Marketing analysis/marketing_data_fixed_pivoted.csv")
```
## Fields investigation
Histograms of all numeric values
```{r,warning=FALSE}
# histograms of all numeric values
market_data_fixed_numeric <- market_data_fixed[,sapply(market_data_fixed, is.numeric)]
market_data_fixed_numeric %>%
  pivot_longer(cols = everything(), names_to="key", values_to="value") %>%
  ggplot(aes(value)) +
  facet_wrap(~key, scales = "free") +
  geom_histogram()  
# boxplots of all numeric values
market_data_fixed_numeric %>%
  pivot_longer(cols = everything(), names_to="key", values_to="value") %>%
  ggplot(aes(value)) +
  facet_wrap(~key, scales = "free") +
  geom_boxplot() 

```

Conclusions: It seems that all distributions are skewed: need to be checked for normality in case of hypothesis check. There are outliers in Income_fixed, Mnt and Num variables, Year_Birth -> can be imputed to make distribution more normal

## Correlation
```{r,warning=FALSE}
# correlation
library(corrplot)
library(RColorBrewer)
corrplot(corr = cor(market_data_fixed_numeric),
         type = "upper",
         col = brewer.pal(n=length(names(market_data_fixed_numeric)),name = "RdYlBu"))
```

Conclusion: Variables with strong correlation should be explored more thoroughly.