---
title: "R Markdown 1"
author: "Andrei Kristov"
date: "1/28/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
It's easy to do slides in R...

***
A slide without heading

## Heading 1
### Heading 2
#### Heading 3

Text

## A slide with lists

- Bullet 1
- Bullet 2

1. Item 1
2. Item 2

## Text formats

Plain text

*italic text*

**bold text**

for (i %in% 1:10) {

}

## R code example 1

**mtcars** data set first 5 rows (comment = '', echo = T)

```{r, comment='', echo=T}

head(mtcars,5 )
```

## R code example 2

**mtcars** data set first 5 rows (eval = F)

```{r, comment='', echo=T, eval=F}

head(mtcars,5 )
```

## R code example 3 (plot)

```{r, echo=TRUE, fig.align='center'}
plot(mtcars$wt, mtcars$mpg, col = 'blue')
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

